SPEI drought SN

### 2017-11-08 analysis/drought/explore_drought_spei_regional.Rmd
set chunk name; change axis text size

### Plot 
```{r}
label_variables <- c('spei1' = '1-month',
                     'spei3' = '3-month',
                     'spei6' = '6-month',
                     'spei12' = '12-month',
                     'spei24' = '24-month',
                     'spei48' = '48-month')

@@

d

# >2000
d2000 <- ggplot(spei_mean_melt2000, aes(x=date, y=value, fill=sign)) +  
  geom_bar(stat = "identity") + 
  facet_wrap(~variable, ncol=1, labeller = as_labeller(label_variables)) + 
  scale_fill_manual(values = c("pos" = "darkblue", "neg" = "red")) +
  theme_bw()  + 
  labs(title= 'Drought evolution for Sierra Nevada (From year 2000)',
    x= '',
    y='SPEI') +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none")

@@

# Explore 3, 6 months scales
```{r}
spei_mean_melt1970 <- spei_mean_melt %>% 
  filter(year >= 1970) %>%
  filter(variable %in% c('spei3', 'spei6'))

d1970 <- ggplot(spei_mean_melt1970, aes(x=date, y=value, fill=sign)) +  
  geom_bar(stat = "identity") + 
  facet_wrap(~variable, ncol=1, labeller = as_labeller(label_variables)) + 
  scale_fill_manual(values = c("pos" = "darkblue", "neg" = "red")) +
  theme_bw()  + 
  labs(title= 'Drought evolution for Sierra Nevada (From year 1970)',
    x= '',
    y='SPEI') +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y")

>>>>

### Plot 
```{r plotspei}
label_variables <- c('spei1' = '1-month',
                     'spei3' = '3-month',
                     'spei6' = '6-month',
                     'spei12' = '12-month',
                     'spei24' = '24-month',
                     'spei48' = '48-month')

@@

d
```

```{r plot_spei2000}
# >2000
d2000 <- ggplot(spei_mean_melt2000, aes(x=date, y=value, fill=sign)) +  
  geom_bar(stat = "identity") + 
  facet_wrap(~variable, ncol=1, labeller = as_labeller(label_variables)) + 
  scale_fill_manual(values = c("pos" = "darkblue", "neg" = "red")) +
  theme_bw()  + 
  labs(title= 'Drought evolution for Sierra Nevada (From year 2000)',
    x= '',
    y='SPEI') +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none")

@@

# Explore 3, 6 months scales
```{r plot_spei1970}
spei_mean_melt1970 <- spei_mean_melt %>% 
  filter(year >= 1970) %>%
  filter(variable %in% c('spei3', 'spei6'))

d1970 <- ggplot(spei_mean_melt1970, aes(x=date, y=value, fill=sign)) +  
  geom_bar(stat = "identity") + 
  facet_wrap(~variable, ncol=1, labeller = as_labeller(label_variables)) + 
  scale_fill_manual(values = c("pos" = "darkblue", "neg" = "red")) +
  theme_bw()  + 
  labs(title= 'Drought evolution for Sierra Nevada (From year 1970)',
    x= '',
    y='SPEI') +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none",
        axis.text=element_text(size=7)) +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y")
